\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[inline]{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
{#1 \vspace{-2pt}}
} 
}

\newcommand{\classesList}[4]{
\item\small{
{#1 #2 #3 #4 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & \textbf{\small #2} \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
\textit{\small#1} & \textit{\small #2} \\
\end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
\item
\begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
\small#1 & \textbf{\small #2}\\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%----------HEADING----------
\begin{center}
\begin{center}
{\Huge \scshape Don Dang} \\[1pt]
\small \raisebox{-0.1\height}{\faPhone\ (817)-307-6088} ~ \href{mailto:donphuocdang@gmail.com}{\raisebox{-0.2\height}{\faEnvelope\ \underline{donphuocdang@gmail.com}}} ~ 
\href{https://www.linkedin.com/in/don-dang/}{\raisebox{-0.2\height}{\faLinkedin\ \underline{https://www.linkedin.com/in/don-dang/}}} ~ 
{\raisebox{-0.2\height}{\faGithub}}
\href{https://github.com/dondangp}{\raisebox{-0.2\height}{\underline{github.com/dondangp}}}
\end{center}
\end{center}
\vspace{-20pt}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{The University of Texas at Arlington}{August 2021 -- December 2024}
{Bachelor of Science in Honors Computer Science}{GPA: \textbf{3.95}}
\resumeItemListStart
\resumeItem{Awards: UTA Dean's List (2021 -- Present), Honors in Computer Science}
\resumeItem{Coursework: Object-Oriented Programming, Data Structures and Algorithms, Fundamentals of Software Engineering}
\resumeItemListEnd
\resumeSubHeadingListEnd
% \resumeItem{Relevant Coursework: Object-Oriented Programming (Java), Data Structures and Algorithms, Discrete Structures}

\vspace{-20pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: JavaScript, TypeScript, C/C++, Java, Python, HTML/CSS, MySQL, Kotlin, C\#, .NET, VBA, ABAP} \\
\textbf{Web \& App Development}{: React, React Native, AngularJS, REST APIs, Node.js, Express, Springboot} \\
\textbf{Developer Tools}{: WCF, Docker, Postman, Azure, Jira, Agile, Linux/UNIX, Git/GitHub, Figma, Android Studio, VSCode} \\
\textbf{Databases \& Data Processing}{: MongoDB, Firebase, pandas, BeautifulSoup4, NumPy, Flask} \\
}}
\end{itemize}
\vspace{-23pt}
%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer Intern}{May 2023 -- Present}
{Bell Flight}{Fort Worth, Texas}
\resumeItemListStart
\resumeItem{Developed an API with \textbf{C\#} \& \textbf{AngularJS} to generate "Analyst Work" tab for Bell's Lab Manager Web Application.}
\resumeItem{Full-scale migrated and debugged an existing application, \textbf{Engineering Labs} using \textbf{AngularJS, C\#, \& TypeScript}.}
\vspace{-13pt}
\resumeItem{Coded an \textbf{automated bot}, which supports operations of the finance team by generating monthly finance reports. Reduced task time from 8 hours to 25 minutes. Bot runs 45 times a year - projected time savings is 842 hours per year.
\vspace{-5pt}
\resumeItem{Developed a \textbf{Python} program utilizing \textbf{pandas} to automate specific data extraction from multiple XML files within a directory. Transfers the extracted data to a \textbf{Data Frame}, dynamically adjusting column widths in the Excel file, which successfully exports the \textbf{Data Frame} to Excel.}
}
\resumeItem{Coded a Web Scraper utilizing \textbf{Python} with \textbf{Selenium} library, which automated tasks to download files dynamically.}
\resumeItemListEnd
\resumeSubheading
{Software Engineer}{March 2023 -- Present}
{Pluto Learning} {Arlington, Texas}
\resumeItemListStart
\resumeItem{Founding Software Engineer at start-up, \textbf{Pluto Learning}, driving the development and implementation of software.}
\resumeItem{Developed the homepage of Pluto Learning using \textbf{React, HTML, CSS, JavaScript}. - www.plutolearning.com}
\resumeItem{Currently implementing the app of Pluto Learning using \textbf{React Native}, which will be deployed on the App/Play store.}
\resumeItemListEnd
\resumeSubheading
{Software Engineer Intern}{October 2022 -- January 2023}
{VK Consultant Group, LLC}{Houston, Texas}
\resumeItemListStart
\resumeItem{Implemented dynamic components using \textbf{React} for VK Career Conversation, LLC website. Designed with \textbf{Canva}
}
\resumeItem{Developed a podcast app called \textbf{LKwithVal} using \textbf{React Native}, which was hosted on App Store and Play Store. }
\vspace{5pt}
\resumeSubHeadingListEnd
\vspace{-16pt}
\resumeSubheading
{Artificial Intelligence Research Assistant}{May 2022 -- Present}
{Software Engineering Research Center}{Arlington, Texas}
\resumeItemListStart
\resumeItem{Implemented a  sketching app using partial screening to predict and search for mobile UI designs with \textbf{100\% accuracy} utilizing \textbf{React} with a team of Ph.D computer scientists.}
\resumeItem{Implemented extensions for web application \textbf{PSDoodle}: drag and drop \& computer vision features.}
\resumeItem{Developed and designed UI/UX using Figma \& translated to dynamic \& responsive web components for \textbf{PSDoodle} with \textbf{React, HTML, CSS, JavaScript.}}
\resumeItemListEnd
\vspace{-15pt}
\vspace{10pt}
\resumeSubheading
{Web Developer}{May 2022 -- August 2022}
{Martyrs Catholic Vietnamese Church}{Arlington, Texas}
\resumeItemListStart
\resumeItem{Modified and updated the church’s homepage \& advertisement page using \textbf{React, HTML, CSS, JavaScript}.}
\resumeItem{Utilized \textbf{BootStrap} to make advertisement websites compatible and responsive for mobile phone users.}
\resumeItemListEnd
\vspace{-15pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-10pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{ACM UTA Web Application} $|$ \emph{React, HTML, CSS, JavaScript}}{January 2023 -- Present}
\resumeItemListStart
\resumeItem{Developed responsive image slider featuring the university’s ACM directors utilizing \textbf{React, HTML, CSS, JavaScript}.}
\vspace{-13pt}
\resumeItem{Designed \textbf{UI/UX} in Figma and \textbf{React website} using TypeScript with navbar \& notifications.}
\resumeItem{Utilized Promises to handle API requests efficiently, ensuring timely updates and fetching real-time information.}
\resumeItemListEnd
\vspace{-15pt}
\resumeProjectHeading
{\textbf{Blazian - Live Currency Converter} $|$ \emph{React, Node, CSS, HTML, Figma, Java}}{April 2023 -- May 2023}
\resumeItemListStart
\resumeItem{Lead a team of 5 and developed a currency converter android application with a team using Android Studios (Java) }
\resumeItem{Converts over 160+ currencies worldwide, which includes an inflation calculator.}
\resumeItem{Designed an aesthetic \textbf{UI wireframe} using Figma, incorporating \textbf{dynamic React components} like buttons, form, and hover, with responsive CSS, featuring techniques like media-queries, keyframes for animations, and box-sizing.}
\resumeItem{Technologies and API’s: \textbf{v6 Exchange Rate API, Google Maps API, Google Analytics API, and AWS API}.}
\resumeItemListEnd 
\vspace{-14pt}
          \vspace{-13pt}
        \vspace{5pt}
    \resumeSubHeadingListEnd
\vspace{-5pt}
\vspace{-13pt}

\vspace{5pt}
\resumeSubHeadingListEnd
\vspace{-5pt}

\end{document}
